EduDataSource

### 2014-12-01 GEMDataSource.Rmd
Cleaned up code to show professor tomorrow

#### Import data from GEM Survey ####

@@

# Edit column names for each dataframe

Clean01 <- plyr::rename(x = Clean01, 
                                      replace = c("ki01d01" = "Year01",
                                                  "country" = "Country"))

Clean02 <- plyr::rename(x = Clean02, 
                                      replace = c("ki02d01" = "Year02",
                                                  "country" = "Country"))

Clean03 <- plyr::rename(x = Clean03, 
                                      replace = c("ki03d01" = "Year03",
                                                  "country" = "Country"))

Clean04 <- plyr::rename(x = Clean04, 
                                      replace = c("ki04d01" = "Year04",
                                                  "ki04ctry" = "Country"))

Clean05 <- plyr::rename(x = Clean05, 
                                      replace = c("KI05D01" = "Year05",
                                                  "KI05ctry" = "Country"))

Clean06 <- plyr::rename(x = Clean06, 
                                      replace = c("KI06D01_mean" = "Year06",
                                                  "KI06CTRY" = "Country"))
Clean07 <- plyr::rename(x = Clean07, 
                                      replace = c("ki07d01_" = "Year07",
                                                  "ki07ctry" = "Country"))

Clean08 <- plyr::rename(x = Clean08, 
                                      replace = c("NES08_D01_MEAN" = "Year08",
                                                  "NES08COUNTRY" = "Country"))

Clean09 <- plyr::rename(x = Clean09, 
                                      replace = c("NES09_D01_MEAN" = "Year09",
                                                  "NES09COUNTRY" = "Country"))

Clean10 <- plyr::rename(x = Clean10, 
                                      replace = c("NES10_D01_MEAN" = "Year10",
                                                  "NES10CRNAME" = "Country"))

#### Merge the data ####
MergedGEM <- merge(CCurrentOwner, CEntreIntention,
                   union("Country", "Year"),
                   all = TRUE)

@@

# Run linear regression R3
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + lm(WayofTeach) + Country, data = CompleteData)

@@

# Create regression output table
labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
            'Annual GDP Growth', 'National Level Avg Perceived Good Opportunities', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities','(Intercept)')

@@

# Omit omitted data from simulation
CompleteData_omit <- na.omit(CompleteDataset)

# Run a least squares regression with Zelig
Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteData_omit, model = "ls")
```

@@

# Set range of PercentPerceived values in simulation
x.out2 <- setx(Z1, PercentPerceived = 9:67)

@@

# Adjust margins
par(mar=c(2,2,2,2))

# Plot simulation
plot(simz2, xlab= 'PercentPerceived')

@@

Estonia
Luxemburg
Slovak Republic

>>>>

############# Import data from GEM Survey #############

@@

# Edit column names for each dataframe
Clean01 <- plyr::rename(x = Clean01, 
                                      replace = c("ki01d01" = "2001",
                                                  "country" = "Country"))

Clean02 <- plyr::rename(x = Clean02, 
                                      replace = c("ki02d01" = "2002",
                                                  "country" = "Country"))

Clean03 <- plyr::rename(x = Clean03, 
                                      replace = c("ki03d01" = "2003",
                                                  "country" = "Country"))

Clean04 <- plyr::rename(x = Clean04, 
                                      replace = c("ki04d01" = "2004",
                                                  "ki04ctry" = "Country"))

Clean05 <- plyr::rename(x = Clean05, 
                                      replace = c("KI05D01" = "2005",
                                                  "KI05ctry" = "Country"))

Clean06 <- plyr::rename(x = Clean06, 
                                      replace = c("KI06D01_mean" = "2006",
                                                  "KI06CTRY" = "Country"))

Clean07 <- plyr::rename(x = Clean07, 
                                      replace = c("ki07d01_" = "2007",
                                                  "ki07ctry" = "Country"))

Clean08 <- plyr::rename(x = Clean08, 
                                      replace = c("NES08_D01_MEAN" = "2008",
                                                  "NES08COUNTRY" = "Country"))

Clean09 <- plyr::rename(x = Clean09, 
                                      replace = c("NES09_D01_MEAN" = "2009",
                                                  "NES09COUNTRY" = "Country"))

Clean10 <- plyr::rename(x = Clean10, 
                                      replace = c("NES10_D01_MEAN" = "2010",
                                                  "NES10CRNAME" = "Country"))

#### Merge Annual GEM data

MergedGEM <- merge(CCurrentOwner, CEntreIntention,
                   union("Country", "Year"),
                   all = TRUE)

@@

# Run linear regression R3
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)

@@

# Create regression output table
labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
            'National Level Avg Perceived Good Opportunities', 'Way of Teaching', 'Austria',
            'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Finland', 'France',
            'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan',
            'Korea (South)', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland',
            'Portugal', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey',
            'United Kingdom','United States', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities', '(Intercept)')

@@

# Omit omitted data from simulation
CompleteData_omit <- na.omit(CompleteData)

# Run a least squares regression with Zelig
Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach, data = CompleteData_omit, model = "ls")

@@

H1 <- hist(CompleteData$PercentPerceived)

# Set range of PercentPerceived values in simulation
x.out2 <- setx(Z1, PercentPerceived = 20:70)

@@

# Adjust margins
par(mar=c(5,5,5,5))

# Plot simulation
plot(simz2, xlab = 'PercentPerceived', ylab = 'PercentIntention | PercentPerceived')

@@

### 2014-12-01 Misc/TrialFile.Rmd
Cleaned up code to show professor tomorrow

@@

# Change merged data from wide to long
LongGEM<- melt(data = Merged9,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Rename columns
names(LongGEM) <- gsub("variable", "Year", names(LongGEM))
names(LongGEM) <- gsub("value", "Support", names(LongGEM))

@@

# Subset LongGEM with the countries we need
subset_data <- subset(LongGEM, Country %in% myvars)

>>>>

### Data for final project

@@

# Change merged data from wide to long
LongGEM<- melt(data = CleanMerge,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Rename columns
names(CleanMerge) <- gsub("variable", "Year", names(CleanMerge))
names(CleanMerge) <- gsub("value", "Support", names(CleanMerge))

@@

# Subset LongGEM with the countries we need  (Why does 2001 and 2010 data disappear?)
subset_data <- subset(CleanMerge, Country %in% myvars)

### 2014-12-01 Source/EduDataSource.Rmd
Cleaned up code to show professor tomorrow

# Edit column names for each dataframe
Clean01 <- plyr::rename(x = Clean01, 
                                      replace = c("ki01d01" = "Year01",
                                                  "country" = "Country"))

Clean02 <- plyr::rename(x = Clean02, 
                                      replace = c("ki02d01" = "Year02",
                                                  "country" = "Country"))

Clean03 <- plyr::rename(x = Clean03, 
                                      replace = c("ki03d01" = "Year03",
                                                  "country" = "Country"))

Clean04 <- plyr::rename(x = Clean04, 
                                      replace = c("ki04d01" = "Year04",
                                                  "ki04ctry" = "Country"))

Clean05 <- plyr::rename(x = Clean05, 
                                      replace = c("KI05D01" = "Year05",
                                                  "KI05ctry" = "Country"))

Clean06 <- plyr::rename(x = Clean06, 
                                      replace = c("KI06D01_mean" = "Year06",
                                                  "KI06CTRY" = "Country"))

Clean07 <- plyr::rename(x = Clean07, 
                                      replace = c("ki07d01_" = "Year07",
                                                  "ki07ctry" = "Country"))

Clean08 <- plyr::rename(x = Clean08, 
                                      replace = c("NES08_D01_MEAN" = "Year08",
                                                  "NES08COUNTRY" = "Country"))

Clean09 <- plyr::rename(x = Clean09, 
                                      replace = c("NES09_D01_MEAN" = "Year09",
                                                  "NES09COUNTRY" = "Country"))

Clean10 <- plyr::rename(x = Clean10, 
                                      replace = c("NES10_D01_MEAN" = "Year10",
                                                  "NES10CRNAME" = "Country"))

@@

>>>>

@@

# Edit column names for each dataframe
Clean01 <- plyr::rename(x = Clean01, 
                                      replace = c("ki01d01" = "2001",
                                                  "country" = "Country"))

Clean02 <- plyr::rename(x = Clean02, 
                                      replace = c("ki02d01" = "2002",
                                                  "country" = "Country"))

Clean03 <- plyr::rename(x = Clean03, 
                                      replace = c("ki03d01" = "2003",
                                                  "country" = "Country"))

Clean04 <- plyr::rename(x = Clean04, 
                                      replace = c("ki04d01" = "2004",
                                                  "ki04ctry" = "Country"))

Clean05 <- plyr::rename(x = Clean05, 
                                      replace = c("KI05D01" = "2005",
                                                  "KI05ctry" = "Country"))

Clean06 <- plyr::rename(x = Clean06, 
                                      replace = c("KI06D01_mean" = "2006",
                                                  "KI06CTRY" = "Country"))

Clean07 <- plyr::rename(x = Clean07, 
                                      replace = c("ki07d01_" = "2007",
                                                  "ki07ctry" = "Country"))

Clean08 <- plyr::rename(x = Clean08, 
                                      replace = c("NES08_D01_MEAN" = "2008",
                                                  "NES08COUNTRY" = "Country"))

Clean09 <- plyr::rename(x = Clean09, 
                                      replace = c("NES09_D01_MEAN" = "2009",
                                                  "NES09COUNTRY" = "Country"))

Clean10 <- plyr::rename(x = Clean10, 
                                      replace = c("NES10_D01_MEAN" = "2010",
                                                  "NES10CRNAME" = "Country"))

CleanMerge <- cbind(names = c(rownames(Clean01), rownames(Clean02), rownames(Clean03),
                              rownames(Clean04), rownames(Clean05), rownames(Clean06),
                              rownames(Clean07), rownames(Clean08), rownames(Clean09),
                              rownames(Clean10)),
                    rbind.fill(list(Clean01, Clean02, Clean03, Clean04, Clean05, Clean06,
                                    Clean07, Clean08, Clean09, Clean10)))

########## Recode Country Names in Annual GEM NES Datasets ##########

# Recode countries
CleanMerge$Country[CleanMerge$Country == "AUSTRALIA"] <- "Australia"
CleanMerge$Country[CleanMerge$Country == "AUSTRIA"] <- "Austria"
CleanMerge$Country[CleanMerge$Country == "BELGIUM"] <- "Belgium"
CleanMerge$Country[CleanMerge$Country == "CANADA"] <- "Canada"
CleanMerge$Country[CleanMerge$Country == "CHILE"] <- "Chile"
CleanMerge$Country[CleanMerge$Country == "CZECH REPUBLIC"] <- "Czech Republic"
CleanMerge$Country[CleanMerge$Country == "DENMARK"] <- "Denmark"
CleanMerge$Country[CleanMerge$Country == "ESTONIA"] <- "Estonia"
CleanMerge$Country[CleanMerge$Country == "FINLAND"] <- "Finland"
CleanMerge$Country[CleanMerge$Country == "FRANCE"] <- "France"
CleanMerge$Country[CleanMerge$Country == "GERMANY"] <- "Germany"
CleanMerge$Country[CleanMerge$Country == "GREECE"] <- "Greece"
CleanMerge$Country[CleanMerge$Country == "HUNGARY"] <- "Hungary"
CleanMerge$Country[CleanMerge$Country == "ICELAND"] <- "Iceland"
CleanMerge$Country[CleanMerge$Country == "IRELAND"] <- "Ireland"
CleanMerge$Country[CleanMerge$Country == "ISRAEL"] <- "Israel"
CleanMerge$Country[CleanMerge$Country == "ITALY"] <- "Italy"
CleanMerge$Country[CleanMerge$Country == "JAPAN"] <- "Japan"
CleanMerge$Country[CleanMerge$Country == "KOREA"] <- "South Korea"
CleanMerge$Country[CleanMerge$Country == "MEXICO"] <- "Mexico"
CleanMerge$Country[CleanMerge$Country == "NETHERLANDS"] <- "Netherlands"
CleanMerge$Country[CleanMerge$Country == "NEW ZEALAND"] <- "New Zealand"
CleanMerge$Country[CleanMerge$Country == "NORWAY"] <- "Norway"
CleanMerge$Country[CleanMerge$Country == "POLAND"] <- "Poland"
CleanMerge$Country[CleanMerge$Country == "PORTUGAL"] <- "Portugal"
CleanMerge$Country[CleanMerge$Country == "SLOVAK REPUBLIC"] <- "Slovak Republic"
CleanMerge$Country[CleanMerge$Country == "SLOVENIA"] <- "SLOVENIA"
CleanMerge$Country[CleanMerge$Country == "SPAIN"] <- "Spain"
CleanMerge$Country[CleanMerge$Country == "SWEDEN"] <- "Sweden"
CleanMerge$Country[CleanMerge$Country == "SWITZERLAND"] <- "Switzerland"
CleanMerge$Country[CleanMerge$Country == "TURKEY"] <- "Turkey"
CleanMerge$Country[CleanMerge$Country == "UNITED KINGDOM"] <- "United Kingdom"
CleanMerge$Country[CleanMerge$Country == "UK"] <- "United Kingdom"

CleanMerge$Country[CleanMerge$Country == "UNITED STATES"] <- "United States"
CleanMerge$Country[CleanMerge$Country == "Korea"] <- "South Korea"
CleanMerge$Country[CleanMerge$Country == "US"] <- "United States"

# This one doesn't work
CleanMerge$Country[CleanMerge$Country == "USA"] <- "United States"

########## Subset Annual GEM NES Datasets ##########

# Create a vector with OECD countries
myvars <- c('Australia', 'Austria', 'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Estonia', 'Finland', 'France', 'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan', 'South Korea', 'Luxemburg', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland', 'Portugal', 'Slovak Republic', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey', 'United Kingdom', 'United States')

# Subset LongGEM with the countries we need
subset_data <- subset(CleanMerge, Country %in% myvars)

# Delete unnecessary column
S1 <- subset_data$names <- NULL

########## Change Column names in Subset Annual GEM NES Dataset ##########

# Change merged data from wide to long
LongGEM<- melt(data = Merged9,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Rename columns
names(LongGEM) <- gsub("variable", "Year", names(LongGEM))
names(LongGEM) <- gsub("value", "Support", names(LongGEM))

# Arrange subset_data by country and year
GrandData <- arrange(subset_data, Country, Year)

GrandData1 <- GrandData[order("Country",)]

########### STUCK #############

FinalData <- merge(FinalGEM, GrandData,
                   union("Country", "Year"))
